The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-20 methods/ms.tex
added John's revision of the cygnus sectoin

\subsection{Comparison to Other Surveys}
\label{sec:motte}
\bf{Claudia's comments:}
In general, this section could use some reorganizing such that it sets out why
this comparison field was chosen first (best available data?), describes any
relevant differences in the datasets (eg filter bandpasses, CO possibly in
MAMBO filter), describes how the comparison was done, and then represents the
results.  It seems out of order at the moment.  A reference for CO
contamination causing detectable contamination (at 850um, not 1mm) is
Hatchell, J., \& Dunham, M.~M.\ 2009, arXiv:0904.1163

Comparison of the BGPS flux density calibration
with SCUBA 850 \mum\ results is complicated by the unknown effect
of the dust spectral index.  However, there are several large-area
surveys with the MAMBO instrument at 1.2 mm with which we can compare.
Figure \ref{fig:CygnusComparison} shows the comparison of fluxes
extracted from our map in the Cygnus Arm with those of
\citet{motte07} (M07).

The figures of the Cygnus-X region presented by \citet{motte07}, obtained at a
central wavelength of 1.2 mm using the 30 meter IRAM telescope, appear nearly
identical to the 1.1 mm Bolocam images.  The MAMBO filter is wider than the
Bolocam filter and includes the CO 2-1 line.  Nevertheless, there is excellent
qualitative agreement between the structure revealed by the two data sets on size
scales to which both are sensitive.

[John - may want to remove N46 and other extended sources from comparison.  This 
paragraph needs cleanup]
Direct comparison with the fluxes listed in M07 is difficult
due to the factor of three difference in the size of the beams used.  For
example, the the brightest source in the Cyg-X region is DR 21.  While M07
quote a peak flux density per beam of 4.2 \jyb for the brightest feature in
the DR 21 complex (their peak N46) and 17.9 Jy in a 0.19 x 0.14 pc box,
BGPS measures a peak flux of 17.5 \jyb (the beam being roughly 35\arcsec\ in
diameter).  Fluxes are best compared using sources that appear compact as
observed with the beam of the IRAM 30 meter telescope. Although we list comparisons
for non-compact sources, our flux calibratio comparison was made using compact sources.
The Bolocam and M07 data sets have flux calibration consistent within about
20\%.

We have convolved the \citet{motte07} fits files\footnote{{\tt
ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a Gaussian
kernel that generates an approximately 35\arcsec\ beam, and compared the
measured fluxes with those from the BGPS.  The results are shown in Figure
\ref{fig:CygnusComparison}.

\Table
{lllllll}
{Comparison of \citet{motte07} IRAM measurements to BGPS measurements
in the Cygnus X region.  The IRAM data has been convolved to the BGPS beam
to make the flux density measurements. [John - what does `scaled' mean?]
%Note:  The \citet{motte07} integration box is given in terms of pc. 
%The assumed distance must be about 1.7 kpc \citep{schneider2006}    % no, it's 1.7kpc stated explicitly
}
{
%Source  &   BGPS           &  Motte \\
%        &   peak m\jyb  &  mJy in box (see Motte+ Table 1)
Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  & Ratio &  Comments \\
      Number &  integrated flux &  \jyb          & \jyb  &       &           \\
}
{tab:CygnusComparison}
{
3  &    1.59 [0.11x0.09] & 2.61      &  2.30  & & DR 17                               \\
11 &    0.34 [0.11x0.06] & 0.48      &  0.50  & & West SW of DR21                     \\
12 &    1.63 [0.11x0.09] & 2.60      &  2.20  & &   "                                 \\
16 &    0.55 [0.12x0.12] & 0.82      &  0.72  & &   "                                 \\
26 &    0.34 [0.20x0.10] & 0.48      &  0.44  & &   "                                 \\
29 &    0.54 [0.25x0.13] & 1.10      &  0.62  & &   "                                 \\
30 &   10.54 [0.15x0.10] &13.5       &  9.80  & & W75(N)                              \\
44 &    8.43 [0.14x0.11] &14.5       & 12.7   & & DR21 (OH)                           \\
46 &   17.90 [0.08x0.03] &18.4       & 15.8   & & DR21 f-f, maser (H2O)               \\
48 &    3.72 [0.17x0.11] & 9.4       &  7.8   & & DR21 (OH)-S                         \\
51 &    2.37 [0.24x0.03] & 5.5       &  4.1   & & DR21 FIR2                           \\
53 &    1.60 [0.14x0.09] & 4.3       &  2.7   & & North of DR21  FIR3                 \\
56 &    0.60 [0.12x0.08] & 0.81      &  0.75  & & SE of DR21 47                       \\
58 &    2.73 [0.23x0.19] & 2.40      &  1.64  & & IRAS 20375+4109                     \\
59 &    0.37 [0.12x0.05] & 1.3       &  0.93  & & East of IRAS 20375+4109             \\
60 &    0.56 [0.16x0.13] & 1.00      &  0.78  & & East of IRAS 20375+4109             \\
61 &    0.23 [0.12x0.09] & 0.60      &  0.49  & & MSX 81.5168+0.01926                 \\
62 &    0.50 [0.18x0.12] & 1.23      &  0.80  & & between 63 \& IRAS 20375+4109       \\
63 &    1.09 [0.08x0.05] & 1.60      &  1.50  & & DR22                                \\
65 &    0.78 [0.16x0.12] & 1.15      &  1.10  & &                                     \\
66 &    0.25 [0.15x0.06] & 0.63      &  0.76  & &                                     \\
68 &    0.84 [0.10x0.10] & 1.01      &  0.94  & &                                     \\
69 &    1.28 [0.47x0.18] & 1.12      &  1.20  & &                                     \\
72 &    0.54 [0.28x0.13] & 0.58      &  0.47  & &                                     \\
}

>>>>

\subsection{Comparison to Other Surveys}
\label{sec:motte}

Comparison of the BGPS flux density calibration with SCUBA 850 \mum\
or ATLASGAL 870 \mum\ results is complicated by the poorly determined
variations in the dust spectral index produced by emissivity variations.
However, there are several large-area surveys with the IRAM 30 meter
telescope at 1.2 mm which can be used for comparison with BGPS to
check overall image quality, pointing, and flux calibration.  The study
of the Cygnus-X region by \citet{motte07} presents one of the largest
fields in the Galactic plane that has been mapped with MABO which overlaps
with the Bolocam survey fields.

The Motte Cygnus-X study used both the 37 element MAMBO and 117 channel
MAMBO-2 instrument on the IRAM 30-meter diameter telescope on Pico Veleta
in Spain.   The FWHM beam size for the observations was 11\arcsec .
The effective passband of the images presented by Motte et al.
is about 70 GHz centered at 240 GHz and thus includes the bright
J = 2--1 CO transition.

The structure of the emission in the Cygnus-X region presented by
\citet{motte07} appear nearly identical to the 1.1 mm Bolocam images
of the same field despite the inclusion of the CO line, the slightly
longer (by about 10\%) longer effective wavelength, and different beam
sizes.   The peak positions also agree to within the errors of the
BGPS survey discussed in this paper.

Direct comparison with the fluxes listed in Motte et al. requires
consideration of the factor of three difference in the size of the beams.
For example, the the brightest source in the Cyg-X region is DR 21.
While Motte et al. quote a peak flux density per beam of 4.2 \jyb for
the brightest feature in the DR 21 complex (their peak N46) and 17.9 Jy
in a $\sim$ 17\arcsec\ by 23\arcsec box (0.19 x 0.14 pc at an assumed
distance of 1.7 kpc; see Motte et al. Table 1 in their Appendix).
BGPS measures a peak flux of 17.5 \jyb in an effective beam roughly
35\arcsec\ in diameter, indicating that the relative calibration is
similar on the brightest source in common to both surveys.   However,
DR 21 is an extended source.  Fluxes are best compared using sources
that appear compact as observed with the beam of the IRAM 30 meter
telescope.

We have convolved the \citet{motte07} fits files\footnote{{\tt
ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a Gaussian
kernel that generates an approximately 35\arcsec\ beam, and compared the
measured fluxes with those from the BGPS.  Additionally, the data values
in Motte et al. are in units of Jankys per pixel, with each pixel subtending
a 4\arcsec\ by 4\arcsec\ area on the sky.  In contrast, the data values
in BGPS are in units of Janskys per beam where the beam is 31\arcsec\
in diameter.   The conversion of units required multiplication of the
convolved images by factor of 8.

The Motte et al. images were convolved with IRAF task
GAUSS using a 3.5 pixel convolution kernel to synthesize maps with an
effective FWHM beam diameter of 35\arcsec ;  the BGPS maps have effective
beam diameter 4\arcsec\ larger than the CSO beam diameter of 31\arcsec\
because of the smearing effects of optical distortion at the edges of the
Bolocam array.  This distortion has not been removed from the Version 1.0
images.  The Bolocam flux calibration is based on the measurement of
primary calibrators using the central pixels of the array which are not
effected by distortion.   The results are shown  in Figure
\ref{fig:CygnusComparison} and tabulated in Table 2.  This figure and
the table shows that BGPS and \citet{motte07} clumps have fluxes
consistent within about 20\% after convolution to a 35\arcsec\ beam and
scaling to Jy/beam.

The average Motte et al. fluxes are larger than the BGPS fluxes by a factor
of 1.23 despite the longer wavelength.  Contamination by the bright
CO J = 2-1 line may account for a few percent of the excess
detected flux by MAMBO.    For a dust spectral index of $-3.5$, the
MAMBO measurements should have detected a flux that is about 35\% lower
than what was seen by BGPS.    If this is a typical spectral index for
the sample of clumps, then the Motte et al. flux calibration may be as
much as 45\% higher than the BGPS fluxes.

\Table
{lllllll}
{Comparison of \citet{motte07} IRAM and BGPS measurements
in the Cygnus X region.  The IRAM data has been convolved
to the BGPS beam and scaled so the units are in Jy/beam.
}
{
%Source  &   BGPS           &  Motte \\
%        &   peak m\jyb  &  mJy in box (see Motte+ Table 1)
Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  & Ratio &  Comments \\
     Number &  integrated flux &  \jyb          & \jyb  &       &           \\
}
{tab:CygnusComparison}
{
3  &    1.59 [0.11x0.09] & 2.61      &  2.30  & & DR 17                               \\
11 &    0.34 [0.11x0.06] & 0.48      &  0.50  & & West SW of DR21                     \\
12 &    1.63 [0.11x0.09] & 2.60      &  2.20  & &   "                                 \\
16 &    0.55 [0.12x0.12] & 0.82      &  0.72  & &   "                                 \\
26 &    0.34 [0.20x0.10] & 0.48      &  0.44  & &   "                                 \\
29 &    0.54 [0.25x0.13] & 1.10      &  0.62  & &   "                                 \\
30 &   10.54 [0.15x0.10] &13.5       &  9.80  & & W75(N)                              \\
44 &    8.43 [0.14x0.11] &14.5       & 12.7   & & DR21 (OH)                           \\
46 &   17.90 [0.08x0.03] &18.4       & 15.8   & & DR21 f-f, maser (H2O)               \\
48 &    3.72 [0.17x0.11] & 9.4       &  7.8   & & DR21 (OH)-S                         \\
51 &    2.37 [0.24x0.03] & 5.5       &  4.1   & & DR21 FIR2                           \\
53 &    1.60 [0.14x0.09] & 4.3       &  2.7   & & North of DR21  FIR3                 \\
56 &    0.60 [0.12x0.08] & 0.81      &  0.75  & & SE of DR21 47                       \\
58 &    2.73 [0.23x0.19] & 2.40      &  1.64  & & IRAS 20375+4109                     \\
59 &    0.37 [0.12x0.05] & 1.3       &  0.93  & & East of IRAS 20375+4109             \\
60 &    0.56 [0.16x0.13] & 1.00      &  0.78  & & East of IRAS 20375+4109             \\
61 &    0.23 [0.12x0.09] & 0.60      &  0.49  & & MSX 81.5168+0.01926                 \\
62 &    0.50 [0.18x0.12] & 1.23      &  0.80  & & between 63 \& IRAS 20375+4109       \\
63 &    1.09 [0.08x0.05] & 1.60      &  1.50  & & DR22                                \\
65 &    0.78 [0.16x0.12] & 1.15      &  1.10  & &                                     \\
66 &    0.25 [0.15x0.06] & 0.63      &  0.76  & &                                     \\
68 &    0.84 [0.10x0.10] & 1.01      &  0.94  & &                                     \\
69 &    1.28 [0.47x0.18] & 1.12      &  1.20  & &                                     \\
72 &    0.54 [0.28x0.13] & 0.58      &  0.47  & &                                     \\
}
% 7
\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
this paper. }{fig:CygnusComparison}{1.0}
